### 2022-01-20 README.Rmd
win init and readme

@@

## RMarkdown files
 - [01_compile_saves](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/01_compile_saves.html)
    + compiles the original coding files into `./data/icb_coder_crisis_sentence_event.tsv`
    + the original coding files are not on the public repository; this can only be run by authors
 - [02_align_sentences](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/02_align_sentences.html)
    + aligns codings from multiple GUI versions on similar source sentences
    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
 - [03_format_and_clean](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/03_format_and_clean.html)
    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
 - [04_aggregation](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/04_aggregation.html)
    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.

 - [05a_data_summary](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/05a_data_summary.html)
    + coding information, sentence root, time, coder confidence
 - [05b_data_summary](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/05b_data_summary.html)
    + actions, speech, thought

>>>>

## Data:

@@

## RMarkdown files
 - 01_compile_saves_and_align
    + compiles the original coding files into `./replication_data/temp/icb_coder_crisis_sentence_event.Rds`
    + the original coding files are not on the public repository; this can only be run by authors
    + aligns codings from multiple GUI versions on similar source sentences
    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
 - 02_format_and_clean
    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
 - 03_aggregation
    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.
